%!TeX program = pdflatex
% Geoff Boeing's Curriculum Vitae
% Email: boeing@usc.edu
% Web: https://geoffboeing.com/
% Repo: https://github.com/gboeing/cv

\documentclass[11pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) for accented characters as single glyph
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % regionalize hyphens, quote marks, etc automatically
\usepackage{microtype}% improve text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto}    % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage{setspace} % custom line spacing
\usepackage{amssymb}

% what is your name?
\newcommand{\myname}{Wenbo Pan}

% select default typefaces
\usepackage{ebgaramond} % document's serif typeface
\usepackage{tgheros}    % document's sans serif typeface

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.7cm}

% define font to use as document's title
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*, family=\sfdefault}{30} % increase sans serif headings tracking
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{30pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

% set page margins (assumes letter paper)
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% set line spacing
\setstretch{0.9}

% define space between list items
\newcommand{\listitemspace}{0.25em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print only the month and year when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    citecolor   = black,
    linkcolor   = black,
    pdfauthor   = {\myname},
    pdfkeywords = {city planning, housing, street networks, transportation, urban design, urban informatics},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
\raggedright{}

% display your name as the document title
\namefont{\myname}

% affiliation and contact info blocks
\vspace{1em}
\begin{minipage}[t]{0.700\textwidth}
% current primary affiliation, left-aligned
No.92, West Dazhi Street \\
Harbin, Heilongjiang, 150001 \\
China
\end{minipage}
\begin{minipage}[t]{0.295\textwidth}
% contact info details, right-aligned
\flushright{}
\href{mailto:pixelwenbo@gmail.com}{pixelwenbo@gmail.com} \\
+86 153 7285 3559 \\
\href{https://panwenbo.icu}{https://panwenbo.icu}
\end{minipage}


\section*{Education}

\begin{tablist}

\item[B.S] \tab{}Computer Science and Technology, Honors School Harbin Institute of Technology (HIT), Harbin China, 2020--Present \\
\item[] \tab{} \textbf{GPA and marks of some selected lessons:}
\item[] \tab{} Overall: 3.64/4.0, Rank: 18/96. \tab{} Machine Learning: 99, Mathematical Logic: 99,  Formal Languages and Automata: 95,  Natural Language Processing: 92.
\end{tablist}

\section*{Research Experience}

\begin{tablist}

\item[July. 2021-] \tab{}Research Center for Social Computing and Information Retrieval, HIT \\
\textit{Research Intern}, Under the guidance of Dr. Libo Qin and Prof. Wanxiang Che \\
Primarily focus on the \textbf{task-oriented dialogue system} and \textbf{spoken language understanding}\\

\item[July. 2021-] \tab{} Department of Cyber Security, HIT \\
\textit{Research Intern}, Under the guidance of Dr. Haining Yu \\
Primarily focus on optimizing the \textbf{homomorphic encryption} methods in \textbf{federated machine learning} process. \\

\item[Oct. 2020 -- Feb. 2021] \tab{} State Key Laboratory of Robotics and Systems, HIT \\
\textit{Research Intern}, Under the guidance of Prof. He Zhang \\ 
Primarily focus on the \textbf{3D reconstruction} and \textbf{target tracking} from the retinal fundus image. \\

\end{tablist}


\section*{Publications}

\subsection*{Preprints}

\begin{tablist}

%\item[\the\year] \tab{}J. Harten and G. Boeing. \enquote{Access to the Exclusive City: Home Sharing as an Affordable Housing Strategy.} \textit{Urban Studies}, under review.

\item[2023] \tab{}A Preliminary Evaluation of ChatGPT for Zero-shot Dialogue Understanding. \\ \textbf{Wenbo Pan}, Qiguang Chen, Xiao Xu, Wanxiang Che and Libo Qin. \textit{(Short paper, arXiv preprint arXiv:2304.04256)}\\

\item[2023] \tab{}End-to-end Task-oriented Dialogue: A Survey of Tasks, Methods, and Future Directions. \\ Libo Qin, \textbf{Wenbo Pan}, Qiguang Chen, Lizi Liao, Zhou Yu, Yue Zhang, Wanxiang Che and Min Li \textit{(Long survey, Under submission)}\\

\end{tablist}

\section*{Honors \& Leadership}

\begin{tablist}

\item[2020-23] \tab{} Second Prize Scholarship(15\%) in the Honor School(3 times), Harbin Institute of Technology;
\item[2022-23] \tab{} President of the HUAWEI Student Association at HIT, Harbin Institute of Technology;
\item[2022] \tab{} Shenzhen International FinTech Competition (FinTechathon), top-10(2\%), WeBank, Shenzhen;
\item[2022] \tab{} Mathematical Contest in Modeling, Honorable Winner. Consortium for Mathematics and Its Application, America;
\item[2021] \tab{} Excellent Student Leader. Harbin Institute of Technology.

\end{tablist}

\section*{Skills}

\begin{enumerate}[label=\textbullet]
    \item \textbf{Languages}: English (IELTS 7.5), Mandarin Chinese (native)
    \item \textbf{Programming Languages}: Python, C++, Javascript, Swift, C\#, Shell
    \item \textbf{Development Tools}: Git, Linux, Vim, Docker, VSCode, \LaTeX
    \item \textbf{Tools for DL}: PyTorch, Huggingface, wandb
    \item \textbf{Others}: Resberry Pi, Arduino, Unity, Video Editing
  \end{enumerate}

% display today's date as Month Year after a vertical space below the end of the text
\begin{center}
    \vfill
    Updated \monthyeardate\today
\end{center}

\end{document}
